Active Object Search with a Mobile Device for the Visually Impaired

### 2018-11-22 paper.tex
Removed unessessary images from git, edit to section 4

\noindent The guidance system is built into an Android app and uses Android's ARCore\footnote{https://developers.google.com/ar/} API to track the device's pose. The system is designed with the goal of generating a path of waypoints for the user to follow, by pointing the device camera, that will lead the user to the target object. This path is generated one waypoint at a time by the system and is updated with every object observation the user makes after adjusting the camera. We modelled and solved the search problem using an MDP model. The details of the model's design and implementation are discussed in the following sections. %For this initial design, the system only works in the pan and tilt dimension and the depth dimension will be added after successful testing of this version of the guidance system.

%\subsection{Environment Model}\label{sec:env-design}

@@

Consider the scene in Figure~\ref{fig:route-example} which contains a number of simple, distinct objects (the red boxes). The MDP's task is to direct the user to point the camera to the target object (the mug in the bottom-left of Figure~\ref{fig:route-example}). It does this by inferring the current state by sampling the object currently within the camera's view, and generates an action that leads the user to the target object. The states are sampled and the actions are generated in discretised steps as the user moves the camera's view in the instructed direction. This discrete behaviour is similar to a waypoint navigation approach where the user goes from one waypoint to the next, until the user points the camera to target object.

@@

The app was developed on and experimented with an Asus ZenPhone AR\footnote{asus.com/uk/Phone/ZenFone-AR-ZS571KL/} running Android version 7.0 with the ARCore SDK enabled. No hardware or software modifications were required.

>>>>

\noindent The system guides a user by generating a set of waypoints to indicate an area for the user to investigate with the camera and will lead the user to the target object. This path is generated one waypoint at a time by the system and is updated with every object observation the user makes after adjusting the camera. We modelled the problem using an MDP and the details of the model's design and implementation are discussed in the following sections. %For this initial design, the system only works in the pan and tilt dimension and the depth dimension will be added after successful testing of this version of the guidance system.
 %The guidance system is built into an Android app and uses Android's ARCore API to track the device's pose. 
%\subsection{Environment Model}\label{sec:env-design}

@@

Consider the scene in Figure~\ref{fig:route-example} which contains a number of simple, distinct objects (the red boxes). The MDP's task is to direct the user to point the camera to the target object (the mug in the bottom-left of Figure~\ref{fig:route-example}). It does this by inferring the current state by sampling the object currently within the camera's view and generates an action that leads the user to the target object. The states are sampled and the actions are generated in discretised steps as the user moves the camera's view in the instructed direction. %This discrete behaviour is similar to a waypoint navigation approach where the user goes from one waypoint to the next, until the user points the camera to target object.

@@

The app was developed on and experimented with an Asus ZenPhone AR\footnote{asus.com/uk/Phone/ZenFone-AR-ZS571KL/} running Android version 7.0 with the ARCore\footnote{https://developers.google.com/ar/} SDK enabled. No hardware or software modifications were required.
